### 2023-11-23 main.tex
''

We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\tau_{x},\sigma_{x}\in \{1,\ldots,N\}$, we have 
	\delta_{\tau_{x},\sigma_{x}}+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})=&\delta_{\tau_{x},\sigma_{x}}(\delta_{\sigma_{x},N}+1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
	=&\delta_{\tau_{x},\sigma_{x}}\delta_{\sigma_{x},N}+\delta_{\tau_{x},\sigma_{x}}(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\nonumber\\
	=&\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\dt

@@

	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\\
	=&\begin{cases}
		(\alpha_{\tau_{x}}-\beta_{\tau_{x}})+\beta_{\tau_{x}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad &\text{if}\quad \tau_{x}= N\dt
Therefore we can replace $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})$ with $(\alpha_{\tau_{x}}-\beta_{\tau_{x}})$ in \eqref{ABS_intermediate}. 

@@

As a consequence we rewrite \eqref{ABS_intermediate} as 

@@

=&\frac{1}{(L+1)!}\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\\&\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\dt

@@

For all $x\in \{1,\ldots,L\}$ we introduce the summation index $c_{x}\in \{\delta_{\tau_{x},N},1\}$ and we have that 
	&\sum_{\sigma_{x}=1}^{N}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}\left[\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+\beta_{\tau_{x}}\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right]\nonumber\\
	\sum_{c_{x}=\delta_{\tau_{x},N}}^{1}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\beta_{\tau_{x}}^{c_{x}(1-\delta_{\tau_{x},N})}
	\sum_{\sigma_{1}=1}^{N}\ldots\sum_{\sigma_{L}=1}^{N}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)=\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}\left(1+\sum_{j=x}^{L}c_{j}\right)\dt
Then, by replacing the summations over $\sigma_{1},\ldots,\sigma_{L}$ by the summations over $c_{1},\ldots,c_{L}$, we obtain  

@@

Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally obtain

@@

>>>>

We observe that, for any fixed $x\in \{1,\ldots,L\}$ and for any fixed $\bm{\tau},\bm{\sigma}\in\Omega^{'}$, we have 
	\left[\delta_{\tau_{x},\sigma_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\beta_{\tau_{x}}\right]\left(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}}\right)^{1-\delta_{\sigma_{x},N}}=	\left[\delta_{\tau_{x},\sigma_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\beta_{\tau_{x}}\right]\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\dt
Indeed, on one hand if $\sigma_{x}\neq N$ only the term $\delta_{\tau_{x},\sigma_{x}}$ does survive in the square bracket, that is non-vanishing only if $\sigma_{x}=\tau_{x}$. On the other hand, if $\sigma_{x}=N$ the quantity $(\alpha_{\sigma_{x}}-\beta_{\sigma_{x}})^{1-\delta_{\sigma_{x},N}}=1=(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-\delta_{\sigma_{x},N}}$. \\
Moreover, we have that 
	\delta_{\sigma_{x},\tau_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\beta_{\tau_{x}}=&\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\tau_{x},\sigma_{x}}+\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})\right)\nonumber\\
	=&\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\tau_{x},N}\delta_{\sigma_{x},N}+(1-\delta_{\tau_{x},N})(1-\delta_{\sigma_{x},N})+(1-\delta_{\tau_{x},N})\delta_{\sigma_{x},N}\right)\nonumber\\
	=&\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)
Indeed: if $\tau_{x}=\sigma_{x}N$, both sides are $1$; if $\tau_{x}\neq N$ and $\sigma_{x}=N$ both sides are $\beta_{\tau_{x}}$; while, in all other cases, both sides are $0$. 

@@

@@

As a consequence we can write \eqref{ABS_intermediate} as 

@@

=&\frac{1}{(L+1)!}\sum_{\bm{\sigma}\in \Omega^{'}}^{N}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-\delta_{\sigma_{x},N}}\left(1+\sum_{j=x}^{L}\delta_{\sigma_{j},N}\right)\nonumber\\&\left[\beta_{\tau_{x}}^{\delta_{\sigma_{x},N}(1-\delta_{\tau_{x},N})}\left(\delta_{\sigma_{x},N}+(1-\delta_{\sigma_{x},N})(1-\delta_{\tau_{x},N})\right)\right]\dt

@@

We observe that the argument of the summation above does not distinguish the colours of the $\sigma$'s but only whether $\sigma_{x}$ is occupied or empty. Therefore, we can replace the summation over $\sigma_{1},\ldots,\sigma_{L}$ with a summation over the indices  $c_{1},\ldots,c_{L}\in \{0,1\}$. Thus, we obtain 
\Psi^{'}(\bm{\tau})	=&\frac{1}{(L+1)!}\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\prod_{x=1}^{L}\left(\alpha_{\tau_{x}}-\beta_{\tau_{x}}\right)^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\left[\beta_{\tau_{x}}^{c_{x}}\left(c_{x}+(1-c_{x})(1-\delta_{\tau_{x},N})\right)\right]\dt
Moreover, because of the term $\delta_{\tau_{x},N}(1-c_{x})$, we can make vary the indices $c_{x}$ in the set $\{\delta_{\tau_{x},N},1\}$. Indeed, when $c_{x}=0$, the addend of the summation is non-vanishing only if $\tau_{x}=N$. Therefore, we obtain 

@@

Observing that $c_{x}(1-\delta_{\tau_{x},N}) =c_{x}-\delta_{\tau_{x},N}$, we finally have

@@

		\Psi^{'}(\bm{\tau})=\frac{1}{(L+1)!}\sum_{c_{1}=\delta_{\tau_{1},N}}^{1}\ldots\sum_{c_{L}=\delta_{\tau_{L},N}}^{1}\prod_{x=1}^{L}(\alpha_{\tau_{x}}-\beta_{\tau_{x}})^{1-c_{x}}\left(1+\sum_{j=x}^{L}c_{j}\right)\beta_{\tau_{x}}^{c_{x}-\delta_{\tau_{x},N}}\dt
